\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}

\usepackage[backend=biber,style=numeric]{biblatex}
\usepackage{csquotes}
\addbibresource{viitteet.bib}

\title{The order of Euler's totient function}
\author{Elli Kiiski}
\date{2021}

\theoremstyle{definition}
\newtheorem{definition}[subsection]{Definition}
\newtheorem{lemma}[subsection]{Lemma}
\newtheorem{theorem}[subsection]{Theorem}

\begin{document}

{\large
Elli Kiiski
\par
\textbf{2021 Kandinalku - The order of Euler's totient function}
}
\vspace{0.5cm}

\section{Introduction}

\textcolor{gray}{Placeholder for some introductory explaining about the subject of this thesis.}

All introduced variables $a, b, c, ...$ are integers, unless stated otherwise. Here the set of natural numbers $\mathbb{N}$ consists of positive integers, meaning $0 \not\in \mathbb{N}$.

\begin{definition}{\emph{Divisibility}}

If $b=ka$ for some integer $k$, $b$ is divisible by $a$. This is denoted by $a \vert b$.

\end{definition}

\begin{theorem}{\emph{Greatest common divisor}}

Let $a \in \mathbb{N}$ and $b \in \mathbb{N}$. There is a unique $d \in \mathbb{N}$ with following properties:

\begin{enumerate}
 \item $d \vert a$ and $d \vert b$
 \item if $c \vert a$ and $c \vert b$, then $c \vert d$
\end{enumerate}

The number $d$ is called the greatest common divisor of $a$ and $b$, denoted by $gcd(a,b) = d$.

\begin{proof}
\textcolor{blue}{LeVeque: thm 2.1, chp 2.1, p. 31}
\end{proof}
\end{theorem}

\begin{definition}\emph{Congruence}

Let $m\not=0$. If $m\vert(a-b)$, we say $a$ is congruent to $b$ modulo $m$. It is denoted by $a\equiv b \pmod{m}$.
\end{definition}

\begin{definition}\emph{Complete residue system}
\textcolor{red}{Joku hyvä määritelmä, joka ei aiheuta tarpeita yhä uusille määritelmille.}
\end{definition}

\begin{definition}{\emph{Prime number}}

Integer $p\in\mathbb{N}$ is a prime, if $p \geq 2$ and for every $k\in\mathbb{N}$ holds that if $k \vert p$ then $k\in{1, p}$. The set of prime numbers is denoted by $\mathbb{P}$.

In other words, all integers greater than $1$, only divisible by themself and $1$, are primes.

%Toisin sanoen alkulukuja ovat kaikki lukua $1$ suuremmat luonnolliset luvut, jotka ovat jaollisia vain itsellään ja luvulla $1$.

\end{definition}

\begin{definition}{\emph{Co-prime}}

If $gcd(a,b) = 1$, $a$ and $b$ are called co-primes or relatively primes.

\end{definition}

\begin{definition}{\emph{Multiplicative number theoretic function}}

Function $f: \mathbb{N} \rightarrow \mathbb{R}$ is called number theoretic function. It is multiplicative if $f(ab) = f(a)f(b)$ when $gcd(a, b)=1$.

\end{definition}

\section{Euler's totient function and its properties}

Euler's totient function is a multiplicative number theoretic function...

\begin{definition}{\emph{Euler's totient function $\phi: \mathbb{N} \rightarrow \mathbb{N}$}}

%\textcolor{blue}{Hardy-Wright: chapter 5.5, p. 63}

It is set that $\phi(1) = 1$. For all $n \geq 2$, $\phi(n)$ is the number of integers $a \in \{1,2,...,n\}$, for which $gcd(a,n) = 1$.

\end{definition}

%That is, the value of the totient function at $n \in \mathbb{N}$ is the number of co-primes of $n$ smaller than it.

That is, the value of $\phi(n)$ is the number of positive co-primes of $n$ less or equal to $n$.

\begin{theorem}
%\textcolor{blue}{Hardy-Wright: chapter 5.5, theorem 60, p. 64}

Euler's totient function is multiplicative:
\begin{equation*}
    gcd(m,n)=1 \quad\Rightarrow\quad \phi(mn)=\phi(m)\phi(n)\,.
\end{equation*}

\begin{proof}
Assume $m>1$, $n>1$ and $gcd(m,n)=1$. Consider the array

\begin{table}[!htb]
    \centering
    \begin{tabular}{ccccc}
        $0$ & $1$ & \dots & $m-2$ & $m-1$ \\
        $m$ & $m+1$ & \dots & $m+(m-2)$ & $m+(m-1)$\\
        \vdots & \vdots & \vdots & \vdots & \vdots\\
        $(n-2)m$ & $(n-2)m+1$ & \dots & $(n-2)m+(m-2)$ & $(n-2)m+(m-1)$\\
        $(n-1)m$ & $(n-1)m+1$ & \dots & $(n-1)m+(m-2)$ & $(n-1)m+(m-1)$
    \end{tabular}
\end{table}

which consists of integers from $0$ to $mn-1$, forming a complete residue system (mod $mn$).

Clearly, each row of the array forms a complete residue system (mod $m$) and all the elements of any column are congruent to each other (mod $m$). Now there are two types of columns: $\phi(m)$ columns containing only co-primes to $m$ and the rest containing none of them. (\textcolor{blue}{lähde?})

Now consider the co-prime columns. Every column forms a complete residue system (mod $n$) (\textcolor{blue}{LeVeque: thm. 3.5, chp. 3.2, p. 52}), meaning each includes $\phi(n)$ elements co-prime to $n$. Counting $\phi(n)$ elements from all the $\phi(m)$ columns we get in total $\phi(m)\phi(n)$ numbers that are relatively prime to both $m$ and $n$.

On the other hand, since $gcd(m,n)=1$, an integer $k$ is co-prime to $mn$ if and only if both $gcd(m,k)=1$ and $gcd(n,k)=1$ are true. Hence there are $\phi(m)\phi(n)$ numbers relatively prime to $mn$. Thus by definition $\phi(mn)=\phi(m)\phi(n)$.

The case $m=1$ or $n=1$ is trivial, since $\phi(1)=1$ and hence $\phi(mn)=\phi(m)\phi(n)$.

\end{proof}

\end{theorem}

\begin{theorem}{\emph{Euler's product formula}}
\label{thm:product}

%\textcolor{blue}{Hardy-Wright: chapter 5.5, theorem 62, p. 64}\\
%\textcolor{red}{Oisko jossain parempi lähde}

\begin{equation*}
    \phi(n) = n \prod_{p \vert n} \left(1 - \frac{1}{p}\right)
\end{equation*}

where $\prod_{p \vert n} \left(1 - \frac{1}{p}\right)$ means the product over \emph{distinct} primes that divide $n$.

\begin{proof}

Assume first that $n = p^k$, where $p\in \mathbb{P}$. Now for every $x$, for which $gdc(p^k,x)>1$, holds $x=mp^{k-1}$ for some $m\in \{1,2,...,p^{k-1}\}$.

Hence
\begin{equation*}
    \phi(n)=\phi(p^k)=p^k-p^{k-1}=p^k-\frac{p^k}{p}=\left(1-\frac{1}{p}\right)p^k=\left(1-\frac{1}{p}\right)n.
\end{equation*}

Then, in the general case, assume $n=p_1^{k_1} p_2^{k_2} \cdot \cdot \cdot p_r^{k_r}=\prod_{i=1}^r p_i^{k_i}$, where $p_1,p_2,...,p_r$ are distinct primes that divide $n$ and $k_1,k_2,...,k_r$ their powers respectively. 

% Toi "their powers" ei oo hyvä, joku kertaluku tai muu käsite pitäis kaivaa siihen

Now, since $\phi$ is a multiplicative function
\begin{align*}
    \phi(n) & = \phi(p_1^{k_1} p_1^{k_1} \cdot \cdot \cdot p_r^{k_r})\\
    & = \phi(p_1^{k_1})\,\phi(p_2^{k_2}) \cdot \cdot \cdot \phi(p_r^{k_r})\\
    & = \left(1-\frac{1}{p_1}\right)p_1^{k_1} \left(1-\frac{1}{p_2}\right)p_2^{k_2} \cdot \cdot \cdot \left(1-\frac{1}{p_r}\right)p_r^{k_r}\\
    & = \prod_{i=1}^r \left(1-\frac{1}{p_i}\right) p_i^{k_i}\\
    & = n \prod_{p \vert n} \left(1 - \frac{1}{p}\right).
\end{align*}

\end{proof}

\end{theorem}

\begin{lemma}
\label{thm:phiprime}
For every $p \in \mathbb{P}$ holds $\phi(p) = p-1$\,.

\begin{proof}

Let $n\in\mathbb{P}$. Now the only prime that divides $n$ is $n$ itself. Hence by the Euler's product formula
\begin{equation*}
    \phi(n) = n \prod_{p \vert n} \left(1 - \frac{1}{p}\right) = n\left(1-\frac{1}{n}\right) = n-1\,.
\end{equation*}

\end{proof}

\end{lemma}

\section{Relevant functions and lemmas}

Building up to the order of the totient function, we must introduce few functions and theorems that are used in the proof of the lower limit. Since all of the results of this chapter serve mainly as tools, proof for many of them is not elaborated.

\begin{theorem}{\emph{Mertens' theorem} (\textcolor{blue}{Hardy-Wright: thm. 429, chp. 22.8, p. 466})}
\label{thm:mertens}

\begin{equation*}
    \lim_{n \rightarrow \infty} \log n \prod_{p\leq n} \left(1-\frac{1}{p}\right) = e^{-\gamma}
\end{equation*}

where $\gamma$ is the Euler's constant.

\begin{proof}

\textcolor{gray}{Placeholder for a sketch of the proof.}

\end{proof}

\end{theorem}

\begin{definition}{\emph{Euler-Mascheroni constant} (\textcolor{blue}{Wolfram MathWorld: Euler-Mascheroni constant} (\textcolor{red}{kelpaakohan lähteeksi}))}

The Euler-Mascheroni constant $\gamma$ equals the limit of the difference of the harmonic series and natural logarithm,
\begin{equation*}
    \gamma=\lim_{n\rightarrow\infty} \left(\sum_{k=1}^n \frac{1}{k} - \log n\right) \approx 0,57721566\,.
\end{equation*}
The constant appears in the Mertens' theorem and later in the lower limit of the totient function, yet more detailed consideration goes beyond the scope of this thesis.

\end{definition}

\begin{definition}{\emph{The sigma-function} (\textcolor{blue}{Hardy-Wright: chp. 16.7, p. 310})}

\begin{equation*}
    \sigma(n)=\sum_{d\vert n} d\,,
\end{equation*}

meaning the value of $\sigma(n)$ is the sum of the divisors of $n$.
\end{definition}

\begin{lemma}
\label{lemma:sigma}
Let $n=p_1^{k_1}p_2^{k_2}\cdots p_r^{k_r}$ be the prime factorization of $n$, where $p_1,p_2,...,p_r$ are distinct primes. Then
\begin{equation*}
    \sigma(n)=\prod_{i=1}^r \frac{p_i^{k_i+1}-1}{p_i-1}\,,
\end{equation*}
also denoted by
\begin{equation*}
    \sigma(n) = \prod_{p\vert n} \frac{p^{k+1}-1}{p-1}\,.
\end{equation*}

\begin{proof}
\textcolor{blue}{Hardy-Wright: thm. 275, chp. 16.7, p. 311 }.
\end{proof}
\end{lemma}

\begin{lemma}
\label{thm:sigmafii}
\begin{equation*}
    \frac{\phi(n)\,\sigma(n)}{n^2}<1
\end{equation*}

\begin{proof}
By the Euler's product formula and lemma \ref{lemma:sigma} we get
\begin{align*}
    \phi(n)\,\sigma(n) & = n\prod_{p\vert n}\left(1-\frac{1}{p}\right) \cdot \prod_{p\vert n} \frac{p^{k+1}-1}{p-1}\\
    & = n\prod_{p\vert n}\left(1-\frac{1}{p}\right) \cdot \prod_{p\vert n} p^k \cdot \prod_{p\vert n} \frac{p-\frac{1}{p^k}}{p-1}\\
    & = n\prod_{p\vert n}\left(1-\frac{1}{p}\right) \cdot n \prod_{p\vert n}\frac{1-\frac{1}{p^{k+1}}}{1-\frac{1}{p}}\\
    & = n^2 \prod_{p\vert n} \left( \frac{1-\frac{1}{p^{k+1}}}{1-\frac{1}{p}} - \frac{1-\frac{1}{p^{k+1}}}{p-1}\right)\\
    & = n^2 \prod_{p\vert n} \frac{p-1-\frac{1}{p^k}+\frac{1}{p^{k+1}}}{p-1}\\
    & = n^2 \prod_{p\vert n} \frac{p-1-(p-1)\frac{1}{p^{k+1}})}{p-1}\\
    & = n^2 \prod_{p\vert n} \left(1-\frac{1}{p^{k+1}}\right) < n^2\,.
\end{align*}
Equivivalently
\begin{equation*}
    \frac{\phi(n)\,\sigma(n)}{n^2}<1\,.
\end{equation*}
\end{proof}
\end{lemma}


\begin{definition}{\emph{Chebyshev function} (\textcolor{blue}{Hardy-Wright: chp. 22.1, p. 451})}

\begin{equation*}
    \vartheta(x)=\sum_{p\leq x} \log p = \log \prod_{p\leq x} p\,,
\end{equation*}
where $x\in\mathbb{R}$ and $p\in\mathbb{P}$.

\end{definition}

\begin{lemma}
\label{lemma:vartheta}
For the function $\vartheta(x)$ holds
\begin{equation*}
    \vartheta(x) < Ax\,,
\end{equation*}
where $x\geq2\in\mathbb{R}$, $A$ is a real constant.

\begin{proof}
\textcolor{blue}{Hardy-Wright: thm. 414, chp. 22.2, p. 453}.
\end{proof}
\end{lemma}

\begin{definition}{\emph{Riemann zeta-function} (\textcolor{blue}{Hardy-Wright: chp. 17.2, p. 320})}

\begin{equation*}
    \zeta(s)=\sum_{n=1}^\infty \frac{1}{n^s}\,,
\end{equation*}
where $s\in\mathbb{R}$.
\end{definition}

\begin{lemma}
\label{lemma:zeta}
For all $s>1\in\mathbb{R}$, 
\begin{equation*}
    \zeta(s)=\prod_p \frac{1}{1-\frac{1}{p^s}}\,.
\end{equation*}
\begin{proof}
\textcolor{blue}{Hardy-Wright: thm. 280, chp. 17.2, p. 320}.
\end{proof}
\end{lemma}

\section{The limits of Euler's totient function}

As shown before, there is an exact formula, the Euler's product formula, for the rather verbally defined totient function $\phi(n)$. Though, using it requires factorization of $n$, which makes it difficult to estimate its size as $n$ gets bigger.

For example, let $n = 2^p - 1 \in \mathbb{P}$ be so called Mersenne prime, meaning also $p \in \mathbb{P}$. By theorem \ref{thm:phiprime} we know $\phi(n) = n - 1$. On the other hand, from Euler's product formula follows that $\phi(n+1) = \phi(2^p) = 2^p(1-\frac{1}{2}) = \frac{2^p}{2} = \frac{n+1}{2}$. Now we see that while $n$ and $n+1$ differ from each other only insignificantly, $\phi(n+1)$ is half the size of $\phi(n)$.

We start by proving the fairly obvious upper limit and then dive into a detailed proof of the lower limit.

\subsection{Upper limit of Euler's totient function}

The maximum value of $\phi(n)$ given $n$ is easy to define with theorem \ref{thm:phiprime}.

\begin{theorem}{\emph{Upper limit of the totient function} (\textcolor{blue}{Hardy-Wright: thm. 326, chp. 18.4, p. 352})}

For every $n \geq 2$ holds $\phi(n) \leq n-1$ and
\begin{equation*}
    \limsup{\frac{\phi(n)}{n}} = 1\,.
\end{equation*}

\begin{proof}

By definition, $\phi(n) \leq n$ beacause there are $n$ elements in the set $\{1,2,...,n\}$. Also, for every $n \geq 2$ holds $gcd(n,n) = n \neq 1$. Thus, $\phi(n) \leq n-1$.

On the other hand, according to theorem \ref{thm:phiprime}, $\phi(p) = p-1$ for every $p\in\mathbb{P}$.
% TÄÄ ON VÄÄRIN SANOA NÄIN
% Because there are infinitely many primes, this means that $n-1$ is, in fact, the limit superior of Euler's totient function.
Now, because there are infinitely many primes (\textcolor{blue}{lähde?}),
\begin{equation*}
    \limsup{\frac{\phi(n)}{n}} = \lim \frac{n-1}{n} = 1\,.
\end{equation*}

\end{proof}

\end{theorem}

\subsection{Lower limit of Euler's totient function}

How small $\phi(n)$ can be as $n$ grows, is much less trivial a question to answer. However, it can be shown that the value of $\phi(n)$ is proportional to $\frac{n}{\log\log n}$. The rest of this paper will cover the proof of the exact limit inferior of the totient function.

\begin{theorem}{\emph{Lower limit of the totient function} (\textcolor{blue}{Hardy-Wright: thm. 328, chp. 18.4, p. 352})}

\begin{equation*}
    \liminf{\frac{\phi(n)\,\log\log n}{n}}=e^{-\gamma}\,,
\end{equation*}
where $\gamma$ is the Euler's constant.

\begin{proof}

%\textcolor{blue}{Hardy-Wright: chapter 22.9, p. 467}
We follow here the proof of theorem $328$ from \textit{Hardy \& Wright: Introduction to the Theory of Numbers}, chapter 22.9, p. 467.

Let's prove the claim by showing $\liminf{f(n)} = 1$, when
\begin{equation*}
    f(n)= \frac{\phi(n)\,e^\gamma \log\log n}{n}\,,
\end{equation*}
and $\gamma$ is the Euler's constant.

The proof is based on finding two functions $F_1(t)$ and $F_2(t)$, the limits of which are both $\lim_{t\rightarrow \infty} F_1(t) = 1$ and $\lim_{t\rightarrow \infty} F_2(t) = 1$. First we show that 
\begin{equation}
\label{eq:first}
    f(n) \geq F_1(\log n)\text{ for all }n\geq 3
\end{equation}
and in the second part that
\begin{equation}
\label{eq:second}
    f(n_j) \leq \frac{1}{F_2(j)}\text{ for some infinite increasing sequence }n_2, n_3,...
\end{equation}

Let $p_1,p_2,...,p_{r-\rho} \leq \log n$ and $p_{r-\rho+1},...,p_r > \log n$ be the prime factors of $n$. In other words, the number $n$ has $r$ prime factors, $\rho$ of which are greater than $\log n$.

Now
\begin{equation*}
    (\log n)^\rho < p_{r-\rho+1} \cdot p_{r-\rho+2} \cdots p_r \leq n\,,
\end{equation*}
which yields
\begin{equation*}
    \rho < \frac{\log n}{\log\log n}\,.
\end{equation*}

Thus, there are less than $\frac{\log n}{\log\log n}$ prime factors greater than $\log n$.

By the Euler's product formula (theorem \ref{thm:product})
\begin{align*}
    \frac{\phi(n)}{n} & = \prod_{i=1}^r\left(1-\frac{1}{p_i}\right)\\
    & = \prod_{i=1}^{r-\rho}\left(1-\frac{1}{p_i}\right) \prod_{i=r-\rho+1}^r\left(1-\frac{1}{p_i}\right)\\
    & = \prod_{p\leq\log n}\left(1-\frac{1}{p}\right) \prod_{p>\log n}\left(1-\frac{1}{p}\right)\\
    & \geq \left(1-\frac{1}{\log n}\right)^\rho \prod_{p\leq\log n}\left(1-\frac{1}{p}\right) \\
    & > \left(1-\frac{1}{\log n}\right)^\frac{\log n}{\log \log n} \prod_{p\leq\log n}\left(1-\frac{1}{p}\right)\,.
\end{align*}

Hence, we can define
\begin{equation*}
    F_1(t)=e^\gamma \log t \left(1-\frac{1}{t}\right)^\frac{t}{\log t} \prod_{p\leq t} \left(1-\frac{1}{p}\right)\,,
\end{equation*}
because by the inequality above
\begin{align*}
    F_1(\log n) & = e^\gamma \log \log n \left(1-\frac{1}{\log n}\right)^\frac{\log n}{\log \log n} \prod_{p\leq \log n} \left(1-\frac{1}{p}\right)\\
    & \leq \frac{\phi(n)}{n} e^\gamma \log\log n = f(n)
\end{align*}
and by the Mertens' theorem (theorem \ref{thm:mertens})
\begin{align*}
    \lim_{t \rightarrow \infty} F_1(t) & = \lim_{t \rightarrow \infty} e^\gamma \log t \left(1-\frac{1}{t}\right)^\frac{t}{\log t} \prod_{p\leq t} \left(1-\frac{1}{p}\right)\\
    & = \lim_{t \rightarrow \infty} e^\gamma \left( 1-\frac{1}{t}\right)^\frac{t}{\log t} \left(\log t \prod_{p\leq t} \left(1-\frac{1}{p}\right) \right)\\
    & = \lim_{t \rightarrow \infty} e^\gamma \left( 1-\frac{1}{t}\right)^\frac{t}{\log t} e^{-\gamma}\\
    & = \lim_{t \rightarrow \infty} \left( 1-\frac{1}{t}\right)^\frac{t}{\log t}\\
    & = 1\,.
\end{align*}

Now we have proved the part (\ref{eq:first}) and showed that
$\liminf{f(n)}\geq 1$.

Next, to prove the part (\ref{eq:second}), let's define
\begin{equation*}
    g(n)=\frac{\sigma(n)}{n\,e^\gamma \log\log n}
\end{equation*}
and show that $g(n_j) \geq F_2(j)$ for an infinite increasing sequence $n_2,n_3\dots$. The desired result will follow from theorem \ref{thm:sigmafii}.

Let
\begin{equation*}
    n_j=\prod_{p\leq e^j} p^j\text{, where } j\geq 2\,.
\end{equation*}

By the lemma \ref{lemma:vartheta}
\begin{equation*}
    \log n_j = \log \prod_{p\leq e^j} p^j = j \log \prod_{p\leq e^j} p = j\,\vartheta(e^j) \leq A\,j\,e^j\,,
\end{equation*}
where $A$ is a real constant.

Hence
\begin{equation*}
\label{eq:lognj}
    \log \log n_j = \log Aje^j = \log A + \log j + \log e^j = \log A + \log j + j\,.
\end{equation*}

Since $n_j$ is the product of all primes smaller than $e^j$ to the power of $j$, by the lemma \ref{lemma:sigma} we have
\begin{equation*}
    \sigma(n_j) = \prod_{p\leq e^j} \frac{p^{j+1}-1}{p-1}
\end{equation*}
and
\begin{equation*}
    \frac{\sigma(n_j)}{n_j} = \prod_{p\leq e^j} \frac{p^{j+1}-1}{(p-1)p^j} = \prod_{p\leq e^j} \frac{p^{j+1}\left(1-\frac{1}{p^{j+1}}\right)}{p^{j+1}\left(1-\frac{1}{p}\right)} = \prod_{p\leq e^j} \frac{1-\frac{1}{p^{j+1}}}{1-\frac{1}{p}}\,.
\end{equation*}

Also, by the lemma \ref{lemma:zeta}
\begin{equation*}
    \prod_{p\leq e^j}\left(1-\frac{1}{p^{j+1}}\right) > \prod \left(1-\frac{1}{p^{j+1}}\right) = \frac{1}{\zeta(j+1)}\,.
\end{equation*}

Now we can define
\begin{equation*}
    F_2(t)=\frac{1}{e^\gamma\,\zeta(t+1)(B+t+\log t)} \prod_{p\leq e^t} \left(\frac{1}{1-\frac{1}{p}}\right)\,,
\end{equation*}
where $B=\log A$ is a suitable real constant.

This is, by combining the results above
\begin{align*}
    F_2(j)& = \frac{1}{e^\gamma\,\zeta(j+1)(B+j+\log j)} \prod_{p\leq e^j} \left(\frac{1}{1-\frac{1}{p}}\right)\\
    & \leq \frac{1}{e^\gamma\,\log \log n_j} \prod_{p\leq e^j} \frac{1-\frac{1}{p^{j+1}}}{1-\frac{1}{p}}\\
    & = \frac{\sigma(n_j)}{n_j\,e^\gamma\,\log \log n_j} = g(n_j)\,.
\end{align*}

By the Mertens' third theorem (theorem \ref{thm:mertens})

\begin{equation*}
    \lim_{t \rightarrow \infty} \prod_{p\leq e^t} \left(\frac{1}{1-\frac{1}{p}}\right) = \lim_{t \rightarrow \infty} \frac{1}{\prod_{p\leq e^t} \left(1-\frac{1}{p}\right)} = \left(\frac{e^{-\gamma}}{\log e^t}\right)^{-1} = e^\gamma\,t
\end{equation*}

and hence
\begin{align*}
    \lim_{t \rightarrow \infty} F_2(t) & = \lim_{t \rightarrow \infty} \frac{1}{e^\gamma\,\zeta(t+1)(B+t+\log t)} \prod_{p\leq e^t} \left(\frac{1}{1-\frac{1}{p}}\right)\\
    & = \lim_{t \rightarrow \infty} \frac{e^\gamma\,t}{e^\gamma\,\zeta(t+1)(B+t+\log t)}\\
    & = \lim_{t \rightarrow \infty} \frac{t}{\zeta(t+1)(B+t+\log t)}\\
    & = \lim_{t \rightarrow \infty} \frac{t}{B+t+\log t}\\
    & = 1\,.
\end{align*}

\textcolor{red}{Zeta-funktion raja-arvo pitää käsitellä!}

By the theorem \ref{thm:sigmafii}
\begin{equation*}
    f(n)\,g(n) = \frac{\phi(n)\,e^\gamma \log\log n}{n} \cdot \frac{\sigma(n)}{n\,e^\gamma \log\log n} = \frac{\phi(n)\sigma(n)}{n^2}<1
\end{equation*}

and since $g(n_j) \geq F_2(j)$

\begin{equation*}
    f(n_j)\leq \frac{1}{F_2(j)}\,.
\end{equation*}

Thus we have proved the part (\ref{eq:second}) and showed that $\liminf{f(n)\leq 1}$.

Altogether, from the parts (\ref{eq:first}) and (\ref{eq:second}), we get that the limit inferior of $f(n)$ must be
\begin{equation*}
    \liminf{\frac{\phi(n)\,e^\gamma \log\log n}{n}}=\liminf{f(n)}=1\,
\end{equation*}
and equivalently
\begin{equation*}
    \liminf{\frac{\phi(n)\,\log\log n}{n}}=e^{-\gamma}\,.
\end{equation*}

\end{proof}

\end{theorem}

\end{document}